Plant-pollintor networks worldwide are composed by the same specific building

### 2021-07-26 Draft/Draft.Rmd
Minor edits on intro and table s1

Traditionally, plant-pollinator research has focused on direct interactions and overlooked indirect interactions such as facilitative or competitive interactions between plants for pollinators [@moeller2004; @sargent2008]. Despite the widespread nature of indirect interactions in ecological communities [@strauss1991], plant-pollinator research often fails to finely capture those indirect interactions with the traditional analytical tools that condense the information either by species (e.g. interaction frequency) or in single topological indices (e.g. nestedness). Nonetheless, the emerging framework of network motifs in plant-pollinator research, the building blocks of a network that depict subsets of interactions [@milo2002], allows to consider both direct and indirect interactions [@simmons2019]. The analysis of the meso-scale in plant-pollinator networks have revealed that the different ecological processes that govern species interactions (e.g., species abundances versus trait-matching) can lead to different patterns of indirect interactions [@simmons2020]. However, the global patterns of indirect interactions in plant-pollinator networks (over- and under- representation of motifs) are still unknown.

Motifs are abstract representations often decoupled from species ecology. Hence, linking the structural properties of the meso-scale with the species ecology can help the understanding of ecological processes. For instance, different motifs can have different ecological meanings [@simmons2019] and the position within a motif can determine the species functional role [@stouffer2012; @baker2015]. However, it is unclear if species ecological and life history traits strongly determines its role within the network of interactions [@coux2016]. For example, large pollinators can forage larger distances [@greenleaf2007], deposit greater pollen quantities [@foldesi2021] and handle complex zygomorphic flowers in comparison with small pollinators that are restricted to lower floral complexity [@gong2009]. How this different pollinator behaviors translate into their interaction topology is unknown. Similarly, recent empirical findings indicate that the meso-scale is the best descriptor of plant reproductive success [@allen2021], but little is known on how plants reproductive strategies shape their position within the network of interactions. Although some studies have evaluated plant reproductive strategies in plant-pollinator networks [@tur2013; @lazaro2020], they are often overlooked in a community context [@devaux2014] and rarely incorporated into plant-pollinator network studies. Hence, exploring how the main plant reproductive strategies integrate with the emergent motif framework can shed light on key aspects of ecosystem functioning.

@@

#vector with number of netw per study
`Number of networks` <- c("6", "2", "3", "1", "1", "1", "1", "2", "1", "1", "8", "16", "6", "2", "4", "1", "3", "1")

#`Network structure` <- c(rep("Web", 22), rep("Metaweb",6))

`First author` <- c("Bartomeus", "Dicks", "Dupont", "Elberling", "Fang", "Inouye", "Lundgren", "Olesen", "Small", "Souza", "Kaiser-Bunbury", "Bartomeus", 
                    "Kaiser-Bunbury", "Kaiser-Bunbury", "Peralta", "Burkle", "Arroyo-Correa", "Bundgaard")

Year <- c(2008,2002,2003,1999,2008,1988, 2005,2002,1976,2017,2017,2008,2011,2010,2006,2013,2019,2003) ###JOSE! This method is prone to error, My Beefun dataset is 2015 and not 2008. ###

#Country <- c("Spain", "England", "Denmark", "Sweden", "China", "Australia", "Greenland", "Mauritius and Azores", #"Canada", "Brasil", "Seychelles", "Spain", "Seychelles",
#"Mauritius", "Argentina", "USA", "New Zealand", "Denmark",  "Denmark", "Japan", "Canada", "Venezuela", "Japan", #"Ecuador", "New Zealand", "Venezuela",
#"USA", "Ecuador")

DOI <- c("https://doi.org/10.1007/s00442-007-0946-1", "https://doi.org/10.1046/j.0021-8790.2001.00572.x", "https://doi.org/10.1111/j.1365-2656.2008.01501.x",
         "https://doi.org/10.1111/j.1600-0587.1999.tb00507.x", "https://doi.org/10.1111/1749-4877.12190", "https://doi.org/10.1111/j.1442-9993.1988.tb00968.x",
         "https://doi.org/10.1657/1523-0430(2005)037[0514:TDAHCW]2.0.CO;2", "https://doi.org/10.1046/j.1472-4642.2002.00148.x",
         "/13960/t4km08d21", "https://doi.org/10.1111/1365-2745.12978", "https://doi.org/10.1038/nature21071", "https://github.com/ibartomeus/BeeFunData",
         "https://doi.org/10.1111/j.1365-2745.2010.01732.x", "https://doi.org/10.1016/j.ppees.2009.04.001", "https://doi.org/10.1111/ele.13510",
         "https://doi.org/10.1126/science.1232728", "https://doi.org/10.1111/1365-2745.13332", "Unpublished, Master thesis")

references <- data.frame(`First author`, Year, `Number of networks`,   DOI)

colnames(references) <- c("First author", "Year", "Number of networks",  "DOI")

>>>>

Traditionally, plant-pollinator research has focused on direct interactions and overlooked indirect interactions such as facilitative or competitive interactions between plants for pollinators [@moeller2004; @sargent2008]. Despite the widespread nature of indirect interactions in ecological communities [@strauss1991], plant-pollinator research often fails to finely capture those indirect interactions with the conventional analytical tools that condense the information either by species (e.g. interaction frequency) or in single topological indices (e.g. nestedness). Nonetheless, the emerging framework of network motifs in plant-pollinator research, the building blocks of a network that depict subsets of interactions [@milo2002], allows to consider both direct and indirect interactions [@simmons2019]. The analysis of motifs (meso-scale) in plant-pollinator networks have revealed that the different ecological processes that govern species interactions (e.g., species abundances versus trait-matching) can lead to different patterns of indirect interactions [@simmons2020]. However, the global patterns of indirect interactions in plant-pollinator networks (over- and under- representation of motifs) are still unknown.

Motifs are abstract representations often decoupled from species ecology. Hence, linking the structural properties of the meso-scale with the species ecology can help the understanding of ecological processes. For instance, different motifs can have different ecological meanings [@simmons2019] and the position within a motif can determine the species functional role [@stouffer2012; @baker2015]. However, it is unclear how the species ecology and life history traits determines the species functional role within the network of interactions [@coux2016]. For example, large pollinators can forage larger distances [@greenleaf2007], deposit greater pollen quantities [@foldesi2021] and handle complex zygomorphic flowers in comparison with small pollinators that are restricted to lower floral complexity [@gong2009]. How this different pollinator behaviors translate into their interaction topology is unknown. Similarly, recent empirical findings indicate that the meso-scale is the best descriptor of plant reproductive success [@allen2021], but little is known on how plants reproductive strategies shape their position within the network of interactions. Although some studies have evaluated plant reproductive strategies in plant-pollinator networks [@tur2013; @lazaro2020], they are often overlooked in a community context [@devaux2014] and rarely incorporated into plant-pollinator network studies. Hence, exploring how the main plant reproductive strategies integrate with the emergent motif framework can shed light on key aspects of ecosystem functioning.

@@

#vector with number of netw per study
`Number of networks` <- c("6", #1
                          "2", #2
                          "3",#3
                          "1",#4
                          "1",#5
                          "1",#6
                          "1",#7
                          "2",#8
                          "1",#9
                          "1",#10
                          "8",#11
                          "16",#12
                          "6",#13
                          "2",#14
                          "4",#15
                          "1",#16
                          "3",#17
                          "1"#18
                          )

`First author` <- c("Bartomeus", #1
                    "Dicks",#2
                    "Dupont",#3
                    "Elberling",#4
                    "Fang",#5
                    "Inouye",#6
                    "Lundgren",#7
                    "Olesen",#8
                    "Small",#9
                    "Souza",#10
                    "Kaiser-Bunbury",#11
                    "Bartomeus",#12
                    "Kaiser-Bunbury",#13
                    "Kaiser-Bunbury",#14
                    "Peralta",#15
                    "Burkle",#16
                    "Arroyo-Correa",#17
                    "Bundgaard"#18
                    )

Year <- c(2008,#1
          2002,#2
          2003,#3
          1999,#4
          2008,#5
          1988,#6
          2005,#7
          2002,#8
          1976,#9
          2017,#10
          2017,#11
          2015,#12
          2011,#13
          2010,#14
          2006,#15
          2013,#16
          2019,#17
          2003#18
          )

Country <- c("Spain", #1
               "England", #2
               "Denmark", #3
               "Sweden", #4
               "China", #5
               "United States", #6
               "Denmark (Greenland)", #7
               "Mauritius and Portugal (Azores)", #8
               "Japan", #9
               "Brazil", #10
               "Seychelles", #11
               "Spain", #12
               "Seychelles", #13
               "Mauritius", #14
               "Argentina", # 15
               "United States", #16
               "New Zealand", #17
               "Denmark" #18
               )

DOI <- c("https://doi.org/10.1007/s00442-007-0946-1", #1
         "https://doi.org/10.1046/j.0021-8790.2001.00572.x", #2
         "https://doi.org/10.1111/j.1365-2656.2008.01501.x", #3
         "https://doi.org/10.1111/j.1600-0587.1999.tb00507.x", #4
         "https://doi.org/10.1111/1749-4877.12190", #5
         "https://doi.org/10.1111/j.1442-9993.1988.tb00968.x", #6
         "https://doi.org/10.1657/1523-0430(2005)037[0514:TDAHCW]2.0.CO;2", #7
         "https://doi.org/10.1046/j.1472-4642.2002.00148.x", #8
         "/13960/t4km08d21", #9
         "https://doi.org/10.1111/1365-2745.12978", #10
         "https://doi.org/10.1038/nature21071", #11
         "https://github.com/ibartomeus/BeeFunData", #12
         "https://doi.org/10.1111/j.1365-2745.2010.01732.x", #13
         "https://doi.org/10.1016/j.ppees.2009.04.001", #14
         "https://doi.org/10.1111/ele.13510", #15
         "https://doi.org/10.1126/science.1232728", #16
         "https://doi.org/10.1111/1365-2745.13332", #17
         "Unpublished, Master thesis" #18
         )

references <- data.frame(`First author`, Year, `Number of networks`, Country,   DOI)

colnames(references) <- c("First author", "Year", "Number of networks", "Country",  "DOI")
